---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidytests

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of tidytests is to provide a tidy implementation of the output from t-tests and proportional tests.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` {r eval=FALSE}
# install.packages("remotes")
remotes::install_github("pstraforelli/tidytests")
```

## Example

The package currently consists of two functions, `pairwise_t_test()` and `pairwise_prop_test()`. Both take a raw data frame as input, and the variables to be used for testing.

### `pairwise_t_test()`

```{r example-pairwise-t-test}
library(tidytests)

pairwise_t_test(iris, Sepal.Length, Species)
```

### `pairwise_prop_test()`

```{r example-pairwise-prop-test}
mydf <- data.frame(smokers = c(rbinom(100, 1, .8),
                               rbinom(70, 1, 0.7),
                               rbinom(50, 1, 0.6)),
                   region = c(rep("A", 100), rep("B", 70), rep("C", 50)))
pairwise_prop_test(mydf, smokers, region)
```
