---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidytests

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of tidytests is to provide a tidy implementation of the output from t-tests and proportional tests.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` {r eval=FALSE}
# install.packages("remotes")
remotes::install_github("pstraforelli/tidytests")
```

## Example

The package's functions follow an iterative process. First, use either one of two functions, `pairwise_t_test()` and `pairwise_prop_test()`. Both take a raw data frame as input, and the variables to be used for testing.

### `pairwise_t_test()`

```{r example-pairwise-t-test}
library(tidytests)

pairwise_t_test(iris, Sepal.Length, Species)
```

### `pairwise_prop_test()`

```{r example-pairwise-prop-test}
set.seed(1) # For reproducibility

mydf <- data.frame(smokers = c(rbinom(100, 1, 0.8),
                               rbinom(70, 1, 0.6),
                               rbinom(50, 1, 0.3)),
                   region = c(rep("A", 100), rep("B", 70), rep("C", 50)))
test_df <- pairwise_prop_test(mydf, smokers, region)
test_df
```

Then filter out comparisons that you do not want to show if they do not pass a threshold of your choice (such as a p-value of 0.05).

```{r}
library(dplyr, warn.conflicts = FALSE)
test_df_sig <- test_df %>% 
  filter(p_value < 0.05, smokers == 1) %>% # Only interested in the % among smokers
  select(higher_group, lower_group) # Don't need the rest of the output for the following steps
```

### `prep_sigmark()`

Use `prep_sigmark()` to combine the summary results of your data frame to the output of `pairwise_*_test()`.

```{r example-prep-sigmark}
# Creating summary output
mydf_summ <- mydf %>% 
  count(smokers, region) %>%
  filter(smokers == 1) %>%
  mutate(perc = n / sum(n))
mydf_summ

# Creating colour vector for upcoming chart
colour_vec <- c("red", "blue", "green", "orange")
names(colour_vec) <- LETTERS[1:4]

mydf_prep <- prep_sigmark(mydf_summ, test_df_sig, region, perc, colour_vec, percent = TRUE, vs_rest = FALSE)
mydf_prep
```

### `geom_sigmark()`

Use `geom_sigmark()` as a geom object for your ggplot2 chart.

```{r geom-sigmark, warning=FALSE}
library(ggplot2)
ggplot(mydf_prep, aes(x = region, y = perc, label = labels, fill = region)) +
  geom_col() +
  coord_flip() +
  geom_sigmark("fill", colour_vec, hjust = 0) +
  ylim(c(0, 1))
```

Note that you will see warnings about the encoding of the significance markers. Those can be ignored.
